\documentclass[11pt]{amsart}
\usepackage[a4paper, margin=2.5cm]{geometry}
\usepackage[utf8]{inputenc}

%%%%Package Info%%%
\usepackage{overpic, amssymb, times, graphicx, tikz-cd}
\usepackage[all]{xy}
\usepackage[backref=page]{hyperref}
\usepackage{verbatim}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,
    urlcolor=blue,
    citecolor=blue,
}
\urlstyle{same}

%%%%Specifying new commands%%%%%%%%%%
\DeclareMathOperator{\spec}{spec}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\coker}{coker}
\DeclareMathOperator{\Span}{span}
\DeclareMathOperator{\sprod}{p}
\DeclareMathOperator{\cop}{cop}
\DeclareMathOperator{\im}{im}
\DeclareMathOperator{\dom}{dom}
\DeclareMathOperator{\Diff}{Diff}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\End}{End}
\DeclareMathOperator{\ind}{ind}
\DeclareMathOperator{\sym}{sym}
\DeclareMathOperator{\Symp}{Symp}
\DeclareMathOperator{\Int}{int}
\DeclareMathOperator{\Ann}{Ann}
\DeclareMathOperator{\Id}{Id}
\DeclareMathOperator{\Maslov}{M}
\DeclareMathOperator{\CZ}{CZ}
\DeclareMathOperator{\bcs}{bcs}
\DeclareMathOperator{\Flow}{Flow}
\DeclareMathOperator{\ASL}{ASL}
\DeclareMathOperator{\SL}{SL}
\DeclareMathOperator{\GL}{GL}
\DeclareMathOperator{\PD}{PD}
\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\rot}{rot}
\DeclareMathOperator{\lk}{lk}
\DeclareMathOperator{\tb}{tb}
\DeclareMathOperator{\wl}{wl}
\DeclareMathOperator{\cycword}{cw}
\DeclareMathOperator{\word}{w}
\DeclareMathOperator{\cross}{cr}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\Diag}{Diag}
\DeclareMathOperator{\const}{const}
\DeclareMathOperator{\Ret}{Ret}
\DeclareMathOperator{\expdim}{expdim}
\DeclareMathOperator{\SFT}{SFT}
\DeclareMathOperator{\Sobalev}{W}
\DeclareMathOperator{\Ltwo}{L^{2}}

\newcommand{\thicc}[1]{\pmb{#1}}
\DeclareMathOperator{\aug}{\thicc{\epsilon}}

\newcommand{\filtration}{\mathcal{F}}
\newcommand{\newRSFT}{PDH}
\newcommand{\Algebra}{\mathcal{A}}
\newcommand{\field}{\mathbb{F}}
\newcommand{\Proj}{\mathbb{CP}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\disk}{\mathbb{D}}
\newcommand{\grad}{\nabla}
\newcommand{\bigO}{\mathcal{O}}
\newcommand{\region}{\mathcal{R}}
\newcommand{\Igrading}{\mathcal{I}_{\Lambda}}
\newcommand{\action}{\mathcal{A}}
\newcommand{\energy}{\mathcal{E}}
\newcommand{\rect}{\mathcal{D}}
\newcommand{\delbar}{\overline{\partial}}
\newcommand{\Cinfty}{\mathcal{C}^{\infty}}
\newcommand{\Rthree}{(\R^{3},\xi_{std})}
\newcommand{\Lie}{\mathcal{L}}
\newcommand{\Sthree}{(S^{3},\xi_{std})}
\newcommand{\Tthree}{(T^{3},\xi_{1})}
\newcommand{\Circle}{S^{1}}
\newcommand{\Lj}{L_{j}}
\newcommand{\lj}{\ell_{j}}
\newcommand{\Lp}{L^{+}}
\newcommand{\Lm}{L^{-}}
\newcommand{\Nde}{N^{(\delta,\,\epsilon)}}
\newcommand{\Njde}{N_{j}^{(\delta,\,\epsilon)}}
\newcommand{\Nab}{N^{(\alpha,\,\beta)}}
\newcommand{\Njab}{N_{j}^{(\alpha,\,\beta)}}
\newcommand{\Bthree}{(B^{3},\xi_{std})}
\newcommand{\LambdaZero}{\Lambda^{0}}
\newcommand{\LambdaPlus}{\Lambda^{+}}
\newcommand{\LambdaMinus}{\Lambda^{-}}
\newcommand{\LambdaPM}{\Lambda^{\pm}}
\newcommand{\SurgL}{M_{\Leg}}
\newcommand{\SurgXi}{\xi_{\Leg}}
\newcommand{\SurgLxi}{(\SurgL, \SurgXi)}
\newcommand{\SurgLxiClosed}{(\SurgLClosed, \SurgXi)}
\newcommand{\SurgLPrime}{\R^{3}_{\Lambda}}
\newcommand{\SurgXiPrime}{\xi_{\Lambda}}
\newcommand{\SurgLxiPrime}{(\SurgLPrime, \SurgXiPrime)}
\newcommand{\pxy}{\pi_{xy}}
\newcommand{\J}{\mathcal{J}}
\newcommand{\SLtwoR}{\SL(2, \R)}
\newcommand{\GLtwoR}{\GL(2, \R)}
\newcommand{\SymptwoR}{\Symp(2, \R)}
\newcommand{\half}{\frac{1}{2}}
\newcommand{\partialCH}{\partial_{CH}}
\newcommand{\partialLCH}{\partial_{LCH}}
\newcommand{\partialRSFT}{\partial_{RSFT}}
\newcommand{\partialSFT}{\partial_{SFT}}
\newcommand{\partialLRSFT}{\partial_{LRSFT}}
\newcommand{\ModSpace}{\mathcal{M}}

\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\s}{\vskip.1in}
\newcommand{\n}{\noindent}

\newcommand{\orbitVS}{V}
\newcommand{\SOT}{(S^{3},\xi_{OT})}
\newcommand{\Mxi}{(M,\xi)}
\newcommand{\MxiOT}{(M_{OT}, \xi_{OT})}
\newcommand{\MxiGamma}{(M, \xi, \Gamma)}
\newcommand{\AOB}{(\Sigma,\Phi)}
\newcommand{\OB}{(B,\Sigma,\Phi)}
\newcommand{\OBOT}{(S^{1}\times[0,1], D^{-}_{S^{1}\times\lbrace\frac{1}{2}\rbrace})}
\newcommand{\Xfancy}{\mathcal{X}}
\newcommand{\Cfancy}{\mathcal{C}}
\newcommand{\Gfancy}{\mathcal{G}}
\newcommand{\Hfancy}{\mathcal{H}}
\newcommand{\Sfancy}{\mathcal{S}}
\newcommand{\HeegaardHandle}{\Hfancy}
\newcommand{\HeegaardSurface}{\Sfancy}
\newcommand{\HeegaardCurve}{\mathbf{c}}
\newcommand{\arrowupgrade}{\twoheadrightarrow}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\vertBand}[2]{B^{v}_{#1, #2}}
\newcommand{\horBand}[2]{B^{h}_{#1, #2}}
\newcommand{\annulus}[1][\epsilon]{A_{#1}}
\newcommand{\Dlinearized}{\mathbf{D}}

\newcommand{\sphere}{\mathbb{S}}
\newcommand{\LagTuple}{\thicc{L}}

\newcommand{\LoopSpace}{\mathcal{L}}
\newcommand{\PathSpace}{\mathcal{P}}

\newcommand{\hypersurface}{\Sigma}
\newcommand{\posRegion}{R^{+}}
\newcommand{\negRegion}{R^{-}}
\newcommand{\posNegRegion}{R^{\pm}}
\newcommand{\Lag}{L}
\newcommand{\posLag}{\Lag^{+}}
\newcommand{\negLag}{\Lag^{-}}
\newcommand{\posNegLag}{\Lag^{\pm}}
\newcommand{\Leg}{\Lambda}
\newcommand{\posLeg}{\Leg^{+}}
\newcommand{\negLeg}{\Leg^{-}}
\newcommand{\thiccLeg}{\thicc{\Leg}}
\newcommand{\thiccPosLeg}{\thicc{\Leg}^{+}}
\newcommand{\thiccNegLeg}{\thicc{\Leg}^{-}}
\newcommand{\thiccPosNegLeg}{\thicc{\Leg}^{\pm}}
\newcommand{\posNegLeg}{\Leg^{\pm}}
\newcommand{\divSet}{\Gamma}
\newcommand{\xiDivSet}{\xi_{\divSet}}

%%%%Theorem Definitions%%%%%%%
\newtheorem{thm}{Theorem}[section]
\newtheorem{theorem}[thm]{Theorem}
\newtheorem{claim}[thm]{Claim}
\newtheorem{ex}[thm]{Example}
\newtheorem{assump}[thm]{Assumptions}
\newtheorem*{obs}{Observation}
\newtheorem*{bd}{Boundary Conditions}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{properties}[thm]{Properties}
\newtheorem{param}[thm]{Parameters}
\newtheorem{defn}[thm]{Definition}
\newtheorem{redef}[thm]{Redefinition}
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{q}[thm]{Question}
\newtheorem{rmk}[thm]{Remark}
\newtheorem{fact}[thm]{Fact}
\newtheorem{facts}[thm]{Facts}
\newtheorem{warn}[thm]{Warning}
\newtheorem{edits}[thm]{Editor notes}
\newtheorem{prob}[thm]{Problem}
\newtheorem{trans}{Translation}

%%%% Formatting %%%%%%%%%
%\topmargin0in \textheight8.7in \textwidth6.5in \oddsidemargin0in
%\evensidemargin0in

\title[Notes on bypasses]{Notes on bypasses}
%\author{Russell Avdek}


\begin{document}

\begin{abstract}
Here we take notes on \cite{HH:Bypass} and translate some of the key terminology into the language of double positive factorizations (DPFs).
\end{abstract}

\maketitle

Throughout $\hypersurface$ is a Weinstein convex hypersurface with decomposition $\posNegRegion, \divSet$. We'll take $\dim \divSet = 2n-1, \dim \hypersurface = 2n$.

Here is our convention for building Lefschetz fibrations: Start with a Lefschetz fibration for $W \times \disk \rightarrow \disk$ inducing an open book on the boundary whose page is $W$ and whose monodromy is trivial. Say that the whose mapping torus portion of the open book is $W \times \Circle$. If we attach a Weinstein handle at some $\Leg \subset W \times \{0\}$ then the Lefschetz fibration extends over the surgered Weinstein manifold so that the core of the handle becomes a Lefschetz thimble. The surgery locus in the boundary is $N_{W}(\Leg) \times [0, 3\epsilon]$ and the boundary of the cocore is $\Leg \times \{0\} \simeq \Leg \times \{3\epsilon\}$. Here $N_{W}(\Leg_{k})$ is a standard Weinstein neighborhood of $\Leg$ in $W$. The $\simeq$ is a Legendrian isotopy coming from our ability to slide boundary of the cocore through the handle.

To build up to a general Lefschetz fibration, we attach $k$ Weinstein handles to the neighborhoods
\begin{equation*}
N_{W}(\Leg_{k}) \times \left[\frac{i-1}{k}, \frac{i-1}{k} + 3\epsilon  \right] \subset W \times \Circle, \quad \Circle = \R / \Z
\end{equation*}
using the $4\epsilon$ neighborhoods with $\epsilon$ small. With this ordering convention the monodromy of the open book on the boundary is
\begin{equation*}
\tau_{\Leg_{k}} \circ \cdots \circ \tau_{\Leg_{1}}: W \rightarrow W.
\end{equation*}

For a double positive factorization (DPF), we have $\posNegRegion$ determined by Lefschetz fibrations with fiber $W$ and ordered collections of (framed) Legendrian spheres $\thiccPosNegLeg = (\posNegLeg_{i})_{i=1}^{k^{\pm}}, \posNegLeg_{i} \subset W$. We identify with boundaries when we have an identifications of the fibers of the Lefschetz fibrations on the $\posNegRegion$ with a fixed $W$ and
\begin{equation*}
\tau_{\thiccPosLeg} := \tau_{\posLeg_{k^{+}}} \circ \cdots \circ \tau_{\posLeg_{1}} = \tau_{\negLeg_{k^{-}}} \circ \cdots \circ \tau_{\negLeg_{1}} =: \tau_{\thiccNegLeg}.
\end{equation*}
Specifically the identification of the monodromies allows us identify the mapping tori
\begin{equation*}
[0, 1] \times W/ \sim^{\pm}, \quad (1, x) \sim^{\pm} (0, \tau_{\thiccPosNegLeg}).
\end{equation*}
From the open book picture, the mapping tori make up all of the $\partial \posNegRegion$ except for the binding. The identification trivially extends over the binding since it is $\partial W$.

\section{Legendrian sum and bypasses}

\subsection{Legendrian sum}

Given a pair $\posNegLeg$ of Legendrians in a contact manifold $\divSet$ intersecting $\xi$-transversely at a single point, we'll define the Legendrian sum using the Lagrangian projection formulation from \cite{HH:Bypass}.

Let $N_{\divSet}(\negLeg \cup \posLeg)$ be a neighborhood in $\divSet$ inside of a subset of the $[0, 4\epsilon]_{t} \times W$ where $W$ is a Weinstein manifold containing a plumbing of two copies of $\disk^{\ast}\sphere^{n-1}$. The $\posNegLeg$ are given by the $0$-sections of the $\disk^{\ast}\sphere^{n-1}$ inside $\{0\} \times W$ and our contact structure is determined by $dt + \beta$ for $\beta$ a Liouville form on $W$. Then define
\begin{equation*}
\negLeg \uplus \posLeg \subset [\epsilon, 2\epsilon] \times W
\end{equation*}
to be the Legendrian lift of the Lagrangian sphere
\begin{equation*}
\tau_{\posLeg} \negLeg = \tau_{\negLeg}^{-1} \posLeg \subset W
\end{equation*}
where $\tau$ is a Dehn twist. Then
\begin{equation*}
F^{\pm\epsilon}(\negLeg \uplus \posLeg) := \Flow_{\partial_{t}}^{\pm \epsilon}(\negLeg \uplus \posLeg) \subset ([0, \epsilon] \cup [2\epsilon, 3\epsilon]) \times W.
\end{equation*}

\subsubsection{Translation}

We'll always think of $\posNegLeg$ as being Legendrian spheres sitting on a single page $W$ of an open book for $\divSet$. We'll always work far from the binding so that we can assume that each $t = t_{0}$ slice of $[-2\epsilon, 2\epsilon] \times W$ also sits in a page. After a slight perturbation of the open book the $(\negLeg \uplus \posLeg)^{\pm \epsilon}$ can be assumed to sit on pages as well.

One key observation is that we have conjugacy relations and a braid relation when $\posNegLeg$ intersect at a single point in $W$,
\begin{equation*}
\tau_{\tau_{\posLeg}\negLeg} = \tau_{\posLeg} \circ \tau_{\negLeg} \circ \tau_{\posLeg}^{-1}, \quad \tau_{\posLeg}\tau_{\negLeg}\tau_{\posLeg} \simeq \tau_{\negLeg}\tau_{\posLeg}\tau_{\negLeg}.
\end{equation*}
Another observation is that if $\posLeg$ is an unknot, then $\negLeg \uplus \posLeg$ will be loose in the ambient contact manifold. In the low dimensional case, $\dim \divSet = 3$, this will be $\negLeg$ both positively and negatively stabilized.


\subsection{Bypass}

\begin{defn}
Bypass attachment data consists of a tuple $(\posNegLeg, \posNegLag)$ for which $\posNegLeg$ is a pair of Legendrians intersecting in a single point and $\posNegLag$ are Lagrangian slice disks in the $\posNegRegion$ for the $\posNegLeg$.
\end{defn}

If we attach a bypass to $[-\epsilon, 0] \times \hypersurface$ at $\{ 0 \} \times \hypersurface$ using the data of $(\posNegLeg, \posNegLag)$ then we get a contact structure on $[-\epsilon, 1] \times \hypersurface$ with $\hypersurface_{1} = \{1\} \times \hypersurface$ described as in \cite[Theorem 5.1.3]{HH:Bypass}:
\be
\item $\posNegRegion_{1}$ is obtained by attaching a Weinstein handle to $\negLeg \uplus \posLeg$ and cutting out standard neighborhoods of the $F^{\mp \epsilon}\posNegLag$.
\item $\divSet_{1}$ is obtained by performing a contact $+1$ surgery on $F^{\mp\epsilon}\posNegLeg$ and a contact $-1$ surgery along $(\negLeg \uplus \posLeg)$.
\item The boundaries of the $\posNegRegion_{1}$ are identified by the contactomorphism $\partial \posRegion_{1} \rightarrow \partial \negRegion_{1}$ obtained by sliding $F^{-\epsilon}\posLeg$ up over $(\negLeg \uplus \posLeg)$ to $F^{\epsilon}\negLeg$.
\ee

\subsubsection{Translation}

In the DPF picture, we assume that the $\posNegLeg$ are the $\posNegLeg_{1} \in \thiccPosNegLeg$ so that
\begin{equation*}
\negLeg \uplus \posLeg = \tau_{\posLeg_{1}}\negLeg_{1}.
\end{equation*}
If we are given a Lefschetz fibration determined by a $\thiccLeg$, then cutting out the disk $\Lag_{1}$ whose boundary is $\Leg_{1}$ amounts to replacing $\thiccLeg = (\Leg_{1}, \dots, \Leg_{k})$ with $(\Leg_{2}, \dots, \Leg_{k})$.

Let's assume that the surgery loci for the $\posNegLeg_{1}$ are within $[\epsilon, 2\epsilon] \times W$. Since we use the $\{ 0 \} \times W$ to identify the fibers of the fibration, let's say that $\negLeg_{1} \uplus \posLeg_{1}$ sits on $\{\epsilon\} \times W$ and that there are no surgery loci in $[0, \epsilon] \times W$.

From the positive region description of $\divSet$, we perform add a negative Dehn twist for the contact $+1$ surgery at $\{ 0 \} \times W$, and have the Weinstein handle attachment locus at $\{ \epsilon \} \times W$. As in step (3) of the definition, we slide the $+1$ surgery locus up through the $\{ \epsilon \} \times W$. Now the $+1$ surgery occurs along $\tau_{\negLeg \uplus \posLeg}\posLeg$ and we compute
\begin{equation*}
\begin{aligned}
\left(\tau_{\tau_{\negLeg \uplus \posLeg}\posLeg}\right)^{-1} &= \left(\tau_{\negLeg \uplus \posLeg} \circ \tau_{\posLeg} \circ \tau_{\negLeg \uplus \posLeg}^{-1} \right)^{-1}= \left(\tau_{\posLeg}\tau_{\negLeg}\tau_{\posLeg}^{-1}\tau_{\posLeg}\tau_{\posLeg}^{-1}\tau_{\negLeg}^{-1}\tau_{\posLeg}\right)^{-1}\\
\end{aligned}
\end{equation*}

We use the pushoff directions ($F^{\pm}$) to determine the order in which twists are added to the modnodromies. To follow step (2) in the definition the monodromies become modified as
\begin{equation*}
\begin{aligned}
\tau_{\posLeg_{k}} \circ \cdots \circ \tau_{\posLeg_{1}} &\mapsto \tau_{\posLeg_{k}} \circ \cdots \circ \tau_{\tau_{\posLeg_{1}}\negLeg_{1}} \circ \tau_{\posLeg_{1}}^{-1} \circ \tau_{\posLeg_{1}}\\
\tau_{\negLeg_{k}} \circ \cdots \circ \tau_{\negLeg_{1}} &\mapsto \tau_{\negLeg_{k}} \circ \cdots \circ \tau_{\negLeg_{1}}^{-1} \circ \tau_{\tau_{\posLeg_{1}}\negLeg_{1}} \circ \tau_{\negLeg_{1}}.
\end{aligned}
\end{equation*}
In the first row the $\tau_{\posLeg_{1}}^{-1}$ is added below the new surgery locus and in the second row the $\tau_{\negLeg_{1}}^{-1}$ is added above. These simplify to
\begin{equation*}
\begin{aligned}
\tau_{\posLeg_{k}} \circ \cdots \circ \tau_{\posLeg_{1}} &\mapsto \tau_{\posLeg_{k}} \circ \cdots \circ \tau_{\tau_{\posLeg_{1}}\negLeg_{1}}\\
\tau_{\negLeg_{k}} \circ \cdots \circ \tau_{\negLeg_{1}} &\mapsto \tau_{\posLeg_{k}} \circ \cdots \circ \tau_{\posLeg_{1}}^{-1} \circ \tau_{\tau_{\posLeg_{1}}\negLeg_{1}} \circ \tau_{\posLeg_{1}}.
\end{aligned}
\end{equation*}



\begin{thebibliography}{}
\begin{comment}

\bibitem[Abb11]{Abbas:JBook}
C. Abbas, \textit{Holomorphic open book decompositions}, Duke Math. J., Vol. 158, p.29-82, 2011.

\bibitem[AbbCH05]{ACH:PlanarWeinstein}
C. Abbas, K. Cieliebak, H. Hofer, \textit{The Weinstein conjecture for planar contact structures in dimension three}, Comment. Math. Helv. 80, p.771–793, 2005.

\bibitem[AS06]{AS:Cotangent}
A. Abbondandolo and M. Schwarz, \textit{On the Floer homology of cotangent bundles}, Comm.
Pure Appl. Math., 59, p.254–316, 2006.

\bibitem[Abo15]{Abouzaid:Viterbo}
M. Abouzaid, \textit{Symplectic cohomology and Viterbo’s theorem}, In ``Free loop
spaces in geometry and topology'', volume 24 of IRMA Lect. Math. Theor. Phys., Eur. Math. Soc., Z\"{u}rich, p.271–485, 2015

\bibitem[Al79]{Ahlfors}
L. Ahlfors, \textit{Complex Analysis: An Introduction to the Theory of Analytic Functions of One Complex Variable}, New York: McGraw-Hill, 1979.


\bibitem[AS08]{AS:Pencil}
D. Auroux and I. Smith, \textit{Lefschetz pencils, branched covers and symplectic invariants}, in \textit{Symplectic 4-manifolds and algebraic surfaces}, Lecture Notes in Math vol. 1938, Springer, Berlin, p.1–53, 2008.

\bibitem[Av11]{Avdek:ContactSurgery}
R. Avdek, \textit{Contact surgery and supporting open books}, Algebr. Geom. Topol. Volume 13, p.1613-1660, 2013.

\bibitem[Av20]{Avdek:Dynamics}
R. Avdek, \textit{Combinatorial Reeb dynamics on punctured contact $3$-manifolds}, to appear in Geom. Topol., arXiv:2005.11428, 2020.

\bibitem[Av21a]{Avdek:Liouville}
R. Avdek, \textit{Liouville hypersurfaces and connect sum cobordisms}, J. Symplectic Geom., Vol. 19, 2021.

\bibitem[Av21b]{Avdek:LSFT}
R. Avdek, \textit{Simplified SFT moduli spaces for Legendrian links}, arXiv:2104.00505, 2021.

\bibitem[Av22a]{Avdek:PDH}
R. Avdek, \textit{A filtered generalization of the Chekanov-Eliashberg algebra}, arXiv:2205.13031, 2022.

\bibitem[Av22b]{Avdek:Software}
R. Avdek, \textit{Legendrian links}, software available at \url{https://github.com/RAvdek/legendrian_links}, 2022.

\bibitem[BH15]{BH:ContactDefinition}
E. Bao and K. Honda, \textit{Semi-global Kuranishi charts and the definition of contact homology}, arXiv:1512.00580, 2015.

\bibitem[BH18]{BH:Cylindrical}
E. Bao and K. Honda, \textit{Definition of cylindrical contact homology in dimension three}, Journ. of Topology, Vol. 11, No. 4, p.1002-1053, 2018.


\bibitem[BM]{SmoothAtlas}
D. Bar-Natan, S. Morrison, et. al, \textit{The Rolfsen knot table}, \url{http://katlas.org/wiki/The_Rolfsen_Knot_Table}

\bibitem[Bj16]{Bjorklund:LCH}
J. Bj\"{o}rklund, \textit{Legendrian contact homology in the product of a punctured Riemann surface and the real line}, Journal of the London Math. Soc., Vol. 94, no 3, p.970-992, 2016.
\end{comment}

\bibitem[BEM15]{BEM:OT}
M. S. Borman, Y. Eliashberg, and E. Murphy, \textit{Existence and classification of overtwisted contact structures in all dimensions}, Acta Math. 215, p.281–361, 2015.

\begin{comment}
\bibitem[B02]{Bourgeois:Thesis}
F. Bourgeois, \textit{A Morse-Bott approach to contact homology}, PhD thesis, Stanford University, 2002.

\bibitem[B03]{Bourgeois:ContactIntro} 
F. Bourgeois, \textit{Introduction to contact homology}, lecture notes available at \url{https://www.imo.universite-paris-saclay.fr/~bourgeois/papers/Berder.pdf}, 2003.

\bibitem[BC14]{BC:Bilinearized}
F. Bourgeois and B. Chantraine, \textit{Bilinearized Legendrian contact homology and the augmentation category}, J. Symplectic Geom., Volume 12, p.553–583, 2014.

\bibitem[BG19]{BG:Bilinearized}
F. Bourgeois and D. Galant, \textit{Geography of bilinearized Legendrian contact homology}, arXiv:1905.12037, 2019.


\bibitem[BM03]{BM:Orientations}
F. Bourgeois and K. Mohnke, \textit{Coherent orientations in symplectic field theory}, Math. Z. 248, p.123-146, 2003.

\bibitem[BEE11]{BEE:Product}
F. Bourgeois, T. Ekholm, and Y. Eliashberg, \textit{Symplectic homology product via Legendrian surgery}, PNAS Volume 108, Number 20, p.8114-8121, 2011.

\bibitem[BEE12]{BEE:LegendrianSurgery}
F. Bourgeois, T. Ekholm, and Y. Eliashberg, \textit{Effect of Legendrain Surgery}, Geom. Topol., Volume 16, Number 1, p.301-389, 2012.

\bibitem[BEHW03]{SFTCompactness}
F. Bourgeois, Y. Eliashberg, H. Hofer, and K. Wysocki, \textit{Compactness results in symplectic field theory}, Geom. Topol., Volume 7, Number 2, p.799-888, 2003.

\bibitem[BN10]{AlgebraicallyOvertwisted}
F. Bourgeois and K. Niederkr{\"u}ger, Towards a good definition of algebraically overtwisted,
Expo. Math. 28, no. 1, 85–100, 2010.

\bibitem[BO09a]{BO:MorseBott}
F. Bourgeois and A. Oancea, \textit{Symplectic homology, autonomous Hamiltonians, and Morse–Bott moduli spaces}, Duke Math. J. 146, p.71–174, 2009.

\bibitem[BO09b]{BO:ExactSequence}
F. Bourgeois and A. Oancea, \textit{An exact sequence for contact- and symplectic homology},
Invent. math., Volume 175, p. 611–680, 2009.

\bibitem[BT82]{BottTu}
R. Bott and L. R. Tu, \textit{Differential forms in algebraic topology}, Graduate Texts in Mathematics 82, Springer-Verlag, 1982.
\end{comment}

\bibitem[BHH]{BHH:GirouxCorrespondence}
J. Breen, K. Honda, and Y. Huang, \textit{The Giroux correspondence in arbitrary dimensions}, arXiv:2307.02317, 2023.

\begin{comment}
\bibitem[CGKS14]{CGKS:Polyfilling}
C. Cao, N. Gallup, K. Hayden, J. M. Sabloff, \textit{Topologically Distinct Lagrangian and Symplectic Fillings}, Math. Research Letters, Vol. 21, p.85-99, 2014.

\begin{comment}
\bibitem[CMP19]{CMP:OT}
R. Casals, E. Murphy, and F. Presas, \textit{Geometric criteria for overtwistedness}, J. Amer. Math. Soc. 32, p.563–604, 2019.


\bibitem[CG86]{CG:Cobordisms}
A. Casson, C. M. Gordon, \textit{Cobordism of classical knots}, from: "{\'A} la recherche de la topologie perdue" (editors L Guillou, A Marin), Progr. Math. 62, Birkh{\"a}user 181, 1986.

\bibitem[CDGG20]{Cthulu}
B. Chantraine, G. Dimitroglou Rizell, P. Ghiggini, and R. Golovko, \textit{Floer theory for Lagrangian cobordisms}, J. Differential Geom. 114 no. 3, p.393–465, 2020.

\bibitem[Ch10]{Chantraine:Concordance}
B. Chantraine, \textit{Lagrangian concordance of Legendrian knots}, Algebr. Geom. Topol. 10, p.63-85, 2010.

\bibitem[Ch10]{Chantraine:Symmetric}
B. Chantraine, \textit{Lagrangian concordance is not a symetric relation}, Quantum Topol. Vol. 6,, p.451-474, 2015.

\bibitem[CS99]{StringTopology}
M. Chas and D. Sullivan \textit{String topology}, preprint (1999), math.GT/9911159

\bibitem[CS04]{CS:StringDiagrams}
M. Chas, and D. Sullivan, \textit{Closed string operators in topology leading to Lie bialgebras and higher string algebra}, The legacy of Niels Henrik Abel, p.771–784, Springer, Berlin, 2004.

\bibitem[C02]{Chekanov:LCH}
Y. Chekanov, \textit{Differential algebra of Legendrian links}, Invent. Math., Volume 150, Number 3, p.441–483, 2002.

\bibitem[CN15]{LegKnotAtlas}
W. Chongchitmate and L. Ng, \emph{The Legendrian knot atlas},
\url{http://www.math.duke.edu/~ng/atlas/}, 2015.

\bibitem[Ci02a]{Cieliebak:Subcritical}
K. Cieliebak, \textit{Subcritical Stein manifolds are split}, arXiv:math/0204351v1, 2002.

\bibitem[Ci02b]{Cieliebak:SubcriticalSH}
K. Cieliebak, \textit{Handle attaching in symplectic homology and the Chord Conjecture}, J.
Eur. Math. Soc., p.115–142, 2002.



\bibitem[CE12]{SteinToWeinstein} 
K. Cieliebak and Y. Eliashberg, \textit{From Stein to Weinstein and back}, volume 59 of American
Mathematical Society Colloquium Publications. American Mathematical Society, Providence, RI,
2012.

\bibitem[CFL20]{CFL:Linfty}
K. Cieliebak, K. Fukaya, and J. Latschev, \textit{Homological algebra related to surfaces with boundary}, Quantum Topol., Vol. 11, p.691–837, 2020.

\bibitem[CL07]{CL:SFTStringTop}
K. Cieliebak and J. Latschev, \textit{The role of string topology in symplectic field theory},  New perspectives and challenges in symplectic field theory, CRM Proc. Lecture Notes, vol. 49, Amer. Math. Soc., p. 113–146, 2009.

\bibitem[CM07]{CM:GW}
K. Cieliebak and K. Mohnke, \textit{Symplectic hypersurfaces and transversality in Gromov-Witten theory}, J. Symplectic Geom. 5, p.281-356, 2007.

\bibitem[CEKSW11]{CEKSW:AugCat}
G. Civan, J. Etnyre, P. Koprowski, J. Sabloff, and A. Walker, \textit{Product structures for Legendrian contact homology}, Math. Proc. Cambridge Philos. Soc., Vol. 150, p.291–311, 2011.

\bibitem[CGH11]{CGH:HFequalsECH}
V. Colin, P. Ghiggini and K. Honda, \textit{Equivalence of Heegaard Floer homology and embedded contact homology via open book decompositions}, Proceedings of the National Academy of Sciences of the United States of America,
Vol. 108, No. 20, p.8100-8105, 2011

\bibitem[CGHH10]{CGHH:Sutures}
V. Colin, P. Ghiggini, K. Honda, and M. Hutchings, \textit{Sutures and contact homology I}, Geom. Topol., Vol. 15, p.1749-1842, 2011.


\bibitem[CHT]{CHT:HF}
V. Colin, K. Honda, Y. Tian, \textit{Applications of higher-dimensional Heegaard Floer homology to contact topology}, https://arxiv.org/abs/2006.05701, 2020.

\bibitem[CET19]{CET:PlusOneFilling}
J. Conway, J. Etnyre, and B. Tosun, \textit{Symplectic fillings, contact surgeries, and Lagrangian disks}, IMRN, 2019.


\bibitem[CKK14]{CKK:TightPlanar}
J. Conway, A. Kaloti, D. Kulkarni, \textit{Tight Planar Contact Manifolds with Vanishing Heegaard Floer Contact Invariants}, arXiv:1409.4055, 2014.

\bibitem[CFC20]{CFC:RelativeContactHomology}
L. C\^{o}t\'{e}, F.S. Fauteux-Chapleau, \textit{Homological invariants of codimension 2 contact submanifolds}, 	arXiv:2009.06738, 2020.


\bibitem[CNS16]{CNS:Concordance}
C. Cornwell, L. Ng, and S. Sivek, \textit{Obstructions to Lagrangian concordance}, Algebr. Geom. Topol., Vol. 16, p.797–824, 2016.

\bibitem[DL19]{DiogoLisi}
L. Diogo and S. Lisi, \textit{Symplectic homology of complements of smooth divisors}, J. Topology 12, p. 967-1030, 2019. 

\bibitem[DE20]{DE:Alexander}
L. Diogo and T. Ekholm, \textit{Augmentations, annuli, and Alexander polynomials}, 	arXiv:2005.09733, 2020.

\bibitem[Di92]{Dimca}
A. Dimca, \textit{Singularities and the topology of hypersurfaces}, Springer-Verlag, New York, 1992.

\bibitem[DR16]{DR:Lifting}
G. Dimitroglou Rizell, \textit{Lifting pseudo-holomorphic polygons to the symplectization of $P \times \R$ and applications}, Quantum Topol. 7, p.29–105, 2016.

\bibitem[DRS20]{DRS:Persistence}
G. Dimitroglou Rizell and M. Sullivan, \textit{The persistence of the Chekanov–Eliashberg algebra}, Sel. Math. New Ser., Vol. 26, 2020.

\bibitem[DF18]{DF:HCompactness}
A. Doicu and U. Fuchs, \textit{A Compactness Result for $\mathcal{H}$-holomorphic Curves in Symplectizations}, arXiv:1802.08991, 2018.

\bibitem[DG04]{DG:Surgery}
F. Ding and H. Geiges, \textit{A Legendrian surgery presentation of contact 3-manifolds}, Math. Proc. Cambridge Philos. Soc.,
Vol. 136, p.583-598, 2004.

\bibitem[DG08]{DG:HandleMoves}
F. Ding and H. Geiges, \textit{Handle moves in contact surgery diagrams}, J. Topology, Volume 2, Number 1, p.105-122, 2008.

\bibitem[Dr04]{Dragnev}
D. Dragnev, \textit{Fredholm theory and transversality for noncompact pseudoholomorphic maps in symplectizations}, Comm. Pure Appl. Math. 57, p.726–763, 2004.

\bibitem[EK07]{Ekholm:FlowTrees}
T. Ekholm, \textit{Morse flow trees and Legendrian contact homology in 1-jet spaces}, Geom. Topol., Vol. 11, p.1083–1224, 2007.

\bibitem[Ek08]{Ekholm:Z2RSFT}
T. Ekholm, \textit{Rational symplectic field theory over $\Z_{2}$ for exact Lagrangian cobordisms}, J. Eur. Math. Soc. (JEMS) 10, p.641–704, 2008.

\bibitem[Ek16]{Ekholm:Nonloose}
T. Ekholm, \textit{Non-loose Legendrian spheres with trivial contact homology DGA}, Journal of Topology, Volume 9, p.826–848, 2016.

\bibitem[Ek16]{Ekholm:SurgeryLectures}
T. Ekholm, \textit{Legendrian surgery formulas and applications}, lecture notes from the SFT-VIII conference available at \url{https://www.mathematik.hu-berlin.de/~wendl/SFT8/program.html}, 2016.

\bibitem[Ek19]{Ekholm:SurgeryCurves}
T. Ekholm, \textit{Holomorphic curves for Legendrian surgery}, arXiv:1906.07228, 2019.

\bibitem[EES09]{EES:Duality}
T. Ekholm, J. B. Etnyre, and J. M. Sabloff, \textit{A duality exact sequence for Legendrian contact
homology}, Duke Math. J., 150(1), p.1–75, 2009.

\bibitem[EES05]{EES:Orientations}
T. Ekholm, J. Etnyre, and M. Sullivan, \textit{Orientations in Legendrian Contact Homology and Exact Lagrangian Immersions}, IJM 16, p.453-532, 2005.

\bibitem[EES05]{EES:LegendriansInR2nPlus1}
T. Ekholm, J. Etnyre, and M. Sullivan, \textit{The contact homology of Legendrian submanifolds of $\R^{2n+1}$}, J. Differential Geom. Volume 71, Number 2, p.177-305, 2005.

\bibitem[EHK16]{EHK:LagrangianCobordisms}
T. Ekholm, K. Honda, and T. K\'{a}lm\'{a}n, \textit{Legendrian knots and exact Lagrangian cobordisms}, J. Eur. Math. Soc. (JEMS), 18(11), p.2627–2689, 2016.

\bibitem[EkN15]{EkholmNg:Subcritical}
T. Ekholm and L. Ng, \textit{Legendrian contact homology in the boundary of a subcritical Weinstein 4-manifold}, J. Differential Geom., Volume 101, Number 1, p.67-157, 2015.

\bibitem[EkN18]{EkholmNg:LSFT}
T. Ekholm and L. Ng, \textit{Higher genus knot contact homology and recursion for colored HOMFLY-PT polynomials}, arXiv:1803.04011, 2018.

\bibitem[ENS18]{ENS:CompleteInvariant}
T. Ekholm, L. Ng, and V. Shende, \textit{A complete knot invariant from contact homology}, Invent. Math., Vol. 211, p.1149–1200, 2018.

\bibitem[E98]{Eliashberg:LCH}
Y. Eliashberg, \textit{Invariants in contact topology}, Proceedings of the International Congress of Mathematicians, Vol. II (Berlin), number Extra Vol. II, p.327–338 (electronic), 1998.

\bibitem[EGH00]{EGH:SFTIntro}
Y. Eliashberg, A Givental, and H. Hofer, \textit{Introduction to symplectic field theory}, Geom. Funct. Anal., Special Volume, Part II, p.560-673, 2000.

\bibitem[El89]{Eliash:OTClassification}
Y. Eliashberg, \textit{Classification of overtwisted contact structures on 3-manifolds}, Invent. Math. 98, p.623-637, 1989.

\bibitem[El91]{Eliash:Filling}
Y. Eliashberg, \textit{On symplectic manifolds with some contact properties}, J. Differential Geom. 33, p.233–238, 1991.

\bibitem[EM02]{EM:Hprinciple}
Y. Eliashberg, N. Michachev, {\em Introduction to the h-principle}, Graduate Studies in Mathematics, Volume 48, American Mathematical Society, Providence, RI (2002)

\bibitem[EP96]{EP:UnknotFIlling}
Y. Eliashberg and L. Polterovich, \textit{Local Lagrangian 2-knots are trivial}, Ann. of Math., Vol. 144, p.61–76, 1996.

\bibitem[Et05]{Etnyre:KnotNotes}
J. Etnyre, \textit{Legendrian and Transversal Knots}, Handbook of Knot Theory Elsevier B. V., p.105-185, 2005.

\bibitem[Et08]{Etnyre:ContactSurgery}
J. Etnyre, \textit{On contact surgery}, Proc. Amer. Math. Soc., Volume 136, p.3355-3362, 2008.

\bibitem[EtGh00]{EG:ReebLinks}
J. Etnyre and R. Ghrist, \textit{Contact Topology and Hydrodynamics III: Knotted Orbits}, Transactions of the Amer. Math. Soc., Vol. 352, No. 12, p. 5781-5794, 2000.

\bibitem[EH01]{EtnyreHonda:Knots}
J. Etnyre and K. Honda, \textit{Knots and Contact Geometry I: Torus Knots and the Figure Eight Knot}, J. Symplectic Geom., Volume 1, Number 1, p.63-120, 2001.

\bibitem[EN18]{EtnyreNg:LCHSurvey}
J. Etnyre and L. Ng, \textit{Legendrian contact homology in $\R^{3}$}, arXiv:1811.10966v3, 2018.

\bibitem[ENS02]{ENS:Orientations}
J. Etnyre, L. Ng and J. Sabloff, \textit{Invariants of Legendrian Knots and Coherent Orientations}, J. Symp. Geom., Vol. 1, No. 2, p.321–367, 2002.

\bibitem[ENV13]{ENV:Twists}
J. Etnyre, L. Ng, and V. Vertesi, \textit{Legendrian and transverse twist knots}, J. Eur. Math. Soc. (JEMS), Volume 15, no. 3, p.969–995, 2013.

\bibitem[EO08]{EO:OBInvariants}
J. Etnyre and B. Ozbagci, \textit{Invariants of contact structures from open books}, Trans. Amer. Math. Soc. Volume 360, Number 6, p.3133–3151, 2008.

\bibitem[EV18]{EV:Satellites}
J. Etnyre and V. Vertesi, \textit{Legendrian satellites}, IMRN, Issue 22, p.7241–7304, 2018.

\bibitem[Fa11]{Fabert:Pants}
O. Fabert, \textit{Obstruction bundles over moduli spaces with boundary and the action filtration in symplectic field theory}, Mathematische Zeitschrift, Volume 269, p.325–372, 2011.


\bibitem[Fl88]{Floer:Morse}
A. Floer, \textit{Morse theory for Lagrangian intersections}, J. Diff. Geometry, p.513-547, 1988.


\bibitem[Fu06]{Fukaya:LagrangianSubmanifolds}
K. Fukaya, \textit{Applications of Floer homology of Lagrangian submanifolds to symplectic topology}, Morse Theoretic Methods in Nonlinear Analysis and in Symplectic Topology (P.
Biran, O. Cornea, eds.), Nato Science Series, Volume 217, p.231-276, 2006.

\bibitem[FOOO09]{FOOO}
K. Fukaya, Y. Oh, H. Ohta and K. Ono, \textit{Lagrangian intersection Floer theory: anomaly
and obstruction, Part II}, AMS/IP Studies in Advanced Mathematics, 46.2. American Mathematical
Society, Providence, RI; International Press, Somerville, MA, 2009.

\bibitem[FT17]{FT:Kuranishi}
K. Fukaya and M. Tehrani, \textit{Gromov-Witten theory via Kuranishi structures}, arXiv:1701.07821, 2017.

\bibitem[G94]{Geiges:DisconnectedBoundary}
H. Geiges, \textit{Symplectic manifolds with disconnected boundary of contact type}, Internat. Math. Res. Notices, p.23–30, 1994.


\bibitem[GZ13]{GZ:FourBall}
H. Geiges and K. Zehmisch, \textit{How to recognize a 4-ball when you see one}, M{\"u}nster J. Math., Volume 6, p.525–554, 2013.

\bibitem[G91]{Giroux:Convexity}
E. Giroux, \textit{Convexit\'{e} en topologie de contact}, Comment. Math. Helv. 66, p.637–677, 1991.

\bibitem[G02]{Giroux:ContactOB}
E. Giroux, \textit{G\'{e}om\'{e}trie de contact: de la dimension trois vers les dimensions sup\'{e}rieures}, Proceedings of the International Congress of Mathematicians, Vol. II, Higher Ed. Press, Beijing, p.405-414, 2002.

\bibitem[Girou17]{Giroux:IdealLiouville}
E. Giroux, \textit{Ideal Liouville Domains - a cool gadget}, J. Symplectic Geom., Volume 18, p.769–790, 2017.
\end{comment}

\bibitem[GP17]{GirouxPardon}
E. Giroux and J. Pardon, \textit{Existence of Lefschetz fibrations on Stein and Weinstein domains}, Geom. Topol., 21, no. 2, 963–997, 2017.

\begin{comment}
\bibitem[Go98]{Gompf:Handlebodies}
R. Gompf, \textit{Handlebody construction of Stein surfaces}, Ann. of Math. 148,
p.619-693, 1998.



\bibitem[GS99]{GS:KirbyCalculus}
R. Gopf and A. Stipsicz, \textit{4-manifolds and Kirby Calculus}, Graduate Studies in Mathematics 20, Amer. Math. Society, Providence, RI, 1999.

\bibitem[Gr85]{Gromov:JCurves}
M. Gromov, \textit{Pseudoholomorphic curves in symplectic manifolds}, Invent. Math, Volume 82, p.307–347, 1985.


\bibitem[G14]{Gutt:Normal}
J. Gutt, \textit{Normal Forms for Symplectic Matrices}, Portugalia Mathematicae, vol. 71, p.109-139, 2014.



\bibitem[Ha02]{Hatcher:AlgebraicTopology}
A. Hatcher, \textit{Algebraic topology}, Cambridge University Press, Cambridge, 2002.

\bibitem[HW]{HW:Cop}
N. Higstons, N. Wahl, {\em Products and coproducts in string topology}, arXiv:1709.06839v1, 2017.

\bibitem[Hi03]{Hind:Filling}
R. Hind, \textit{Stein fillings of lens spaces}, Commun. Contemp. Math. 5, no. 6, p.967–982, 2003.

\bibitem[Hof93]{Hofer:OTWeinstein}
H. Hofer, \textit{Pseudoholomorphic curves in symplectizations with applications to the Weinstein conjecture in dimension three}, Inv. Math., Volume 114, p.515-563, 1993.


\bibitem[HWZ96]{HWZ:Asymptotics}
H. Hofer, K. Wysocki and E. Zehnder, \textit{Properties of pseudoholomorphic curves in symplectizations I: Asymptotics}, Ann. Inst. H. Poincar{`e} Anal. Non Lin{`e}aire 13, p.337–37, 1996.

\bibitem[H00]{Honda:Tight1}
K. Honda, \textit{On the classification of tight contact structures I}, Geom. Topol., Volume 4, Number 1, p.309-368, 2000.

\bibitem[Hon00]{Honda:Tight2}
K. Honda, \textit{On the classification of tight contact structures II}, J. Differential Geom., Volume 55, Number 1, p.83-143, 2000.

\bibitem[Hon02]{Honda:OTSurgery}
K. Honda, \textit{Gluing tight contact structures}, Duke Math. J.
Volume 115, Number 3, p.435-478, 2002.

\bibitem[HKM09]{HKM:ContactClass}
K. Honda, W. Kazez, and G. Mati\'{c}, \textit{On the contact class in Heegaard Floer homology}, J. Differential Geom. Volume 83, Number 2, p.289-311, 2009.
\end{comment}

\bibitem[HH18]{HH:Bypass}
K. Honda and H. Huang, \textit{Bypass attachments in higher-dimensional contact topology}, preprint, arXiv:1803.09142, 2018.

\bibitem[HH19]{HH:Convex}
K. Honda and H. Huang, \textit{Convex hypersurface theory in contact topology}, preprint, arXiv:1907.06025, 2019.

\bibitem[HT22]{HT:Category}
Ko Honda and Yin Tian, \textit{Contact categories of disks}, J. Symp. Geom., Vol. 20, 2022.

\begin{comment}
\bibitem[Hua13]{Huang:OTClassification}
Y. Huang, \textit{A proof of the classification theorem of overtwisted contact structures via convex surface theory}, J. Symplectic Geom.
Volume 11, Number 4, p.563-601, 2013.


\bibitem[Hum97]{Hummel}
C. Hummel, \textit{Gromov’s compactness theorem for pseudo-holomorphic curves}, Progress in Mathematics, 151, Birkh\"{a}user Verlag, Basel, 1997.

\bibitem[Hut13]{Hutchings:QOnly}
M. Hutchings, \textit{Rational SFT using only q variables}, blog post available at \url{https://floerhomology.wordpress.com/2013/04/23/rational-sft-using-only-q-variables/}, 2013.

\bibitem[Hut14]{Hutchings:ECHNotes}
M. Hutchings, \textit{Lecture Notes on Embedded Contact Homology}, in Contact and Symplectic Topology, Bolyai Society Mathematical Studies, vol 26, Springer, p.389-484, 2014.

\bibitem[HS06]{HS:T3}
M. Hutchings and M. Sullivan, \textit{Rounding corners of polygons and the embedded contact homology of $T^3$}, Geometry and Topology, Vol. 10, p. 169-266, 2006.


\bibitem[HT07]{HT:GluingI}
M. Hutchings and C. Taubes, \textit{Gluing pseudoholomorphic curves along branched covered cylinders I}, J. Symplectic Geom. 5, p.43–137, 2007.

\bibitem[HT09]{HT:GluingII}
M. Hutchings and C. Taubes, \textit{Gluing pseudoholomorphic curves along branched covered cylinders II}, J. Symplectic Geom. 7, p.29-133, 2009.

\bibitem[Kar20]{Karlsson:Orientations}
C. Karlsson, \textit{A note on coherent orientations for exact Lagrangian cobordisms}, Quantum
Topol., 11(1), p.1–54, 2020.

\bibitem[K87]{Kauffman}
L. H. Kauffman, \textit{State models and the Jones polynomial}, Topology, Volume 26, Number 3, p.395–407, 1987.

\bibitem[Ko00]{Khovanov}
M. Khovanov, \textit{A categorification of the Jones polynomial}, Duke Math. J., Volume 101, Number 3, p.359-426, 2000.

\bibitem[KM93]{KM:MilnorConj}
P. Kronheimer and T. Mrowka. \textit{Gauge theory for embedded surfaces I}. Topology, 32, p.773–826, 1993.

\bibitem[KLT10]{KLT:HFSW}
C. Kutluhan, Y.-J. Lee, and C. Taubes, \textit{HF=HM I: Heegaard Floer homology and Seiberg-Witten Floer homology}, arXiv:1007.1979, 2010.

\bibitem[La93]{Lang142}
S. Lang, \textit{Real and functional analysis}, Graduate texts in mathematics 142, Springer, 1993.

\bibitem[LW11]{LW:Torsion}
J. Latschev and C. Wendl, \textit{Algebraic torsion in contact manifolds (with
an appendix by M. Hutchings)}, Geom. Funct. Anal., Vol. 21, p.1144–1195, 2011.

\bibitem[Li06]{Lipshitz:Cylindrical}
R. Lipshitz. \textit{A cylindrical reformulation of Heegaard Floer homology}, Geometry and Topology, Vol. 10, p.955–1097, 2006.

\bibitem[LOT18]{LOT:Bordered}
R. Lipshitz, P. Ozsv{\'a}th, and D. Thurston, \textit{Bordered Heegaard Floer homology: Invariance and pairing}, Mem. Amer. Math. Soc. 254, no. 1216, 2018.

\bibitem[L98]{Lisca:Nonfillable}
P. Lisca, \textit{Symplectic fillings and positive scalar curvature}, Geom. Topol. 2, p.103-116, 1998.

\bibitem[L08]{Lisca:Filling}
P. Lisca, On symplectic fillings of lens spaces, Trans. Amer. Math. Soc. 360, no. 2, p.765–799, 2008.

\bibitem[LS04]{LS:TightI}
P. Lisca and A. I. Stipsicz, \textit{Ozsváth–Szábo invariants and tight contact three-manifolds I}, Geom. Topol., Volume 8, Number 2, p.925-945, 2004.

\bibitem[LS06]{LS:ContactClassNotes}
P. Lisca and A. I. Stipsicz, \textit{Notes on the Contact Ozsváth-Szabó Invariants}, Pacific J. Math, Volume 228, Number 2, p.277–295, 2006.

\bibitem[L02]{Liu:Moduli}
C.C.M. Liu, \textit{Moduli of J-holomorphic curves with Lagrangian boundary conditions and open Gromov-Witten invariants for an $\Circle$-equivariant pair}, Ph.D. thesis (Harvard University), arXiv:math.SG/0210257, 2002.

\bibitem[Lo02]{Long:Index}
Y. Long, \textit{Index theory for symplectic paths with applications}, volume 207 of
Progress in Mathematics. Birkh\"{a}user Verlag, Basel, 2002.

\bibitem[MNW13]{MNW13}
P. Massot, K. Niederkr\"{u}ger, and C. Wendl, \textit{Weak and strong fillability of higher dimensional contact manifolds}, Invent. math. (2013), 192-287.

\bibitem[M90]{McDuff:RationalRuled}
D. McDuff, \text{The structure of rational and ruled symplectic 4-manifolds}, J. Amer. Math. Soc. 3, p.679–712, 1990.

\bibitem[M91]{McDuff:Filling}
D. McDuff, Symplectic manifolds with contact type boundaries, Invent. Math. 103, p.651–671, 1991.

\bibitem[MS99]{MS:SymplecticIntro}
D. McDuff and D. Salamon, \textit{Introduction to symplectic topology}, Second edition. Oxford Mathematical Monographs. The Clarendon Press, Oxford University Press, New York, 1998.

\bibitem[MS04]{MS:Curves}
D. McDuff and D. Salamon, \textit{J-holomorphic curves and symplectic topology}, American Mathematical Society, Providence, RI, 2004.

\bibitem[MZ20]{MZ:Torsion}
A. Moreno and Z. Zhou, \textit{A landscape of contact manifolds via rational SFT}, 	arXiv:2012.04182, 2020.

\bibitem[N01]{Ng:Satellites}
L. Ng, The Legendrian satellite construction, arXiv:math/0112105, 2001.

\bibitem[N03]{Ng:ComputableInvariants}
L. Ng, \textit{Computable Legendrian invariants}, Topology, Volume 42, p.55–82, 2003.

\bibitem[N10]{Ng:RSFT}
L. Ng, \textit{Rational symplectic field theory for Legendrian knots}, Invent. math., Volume 182, Issue 3, p.451–512, 2010.

\bibitem[N14]{Ng:KCHIntro}
L. Ng, \textit{A topological introduction to knot contact homology}, In Contact and Symplectic Topology, Bolyai Soc. Math. Stud. 26 (Springer, Berlin) 2014.

\bibitem[N]{Ng:Software}
L. Ng et al., \textit{Programs and packages}, \url{https://services.math.duke.edu/~ng/math/programs.html}.

\bibitem[NR13]{NR:Helix}
L. Ng and D. Rutherford, \textit{Satellites of Legendrian knots and representations of the Chekanov–Eliashberg algebra}, Algebr. Geom. Topol., Volume 13, Number 5, p.3047-3097, 2013.

\bibitem[N06]{N:Plastik}
Klaus Niederkr\"{u}ger, \textit{The plastikstufe -- a generalization of the overtwisted disk to higher dimensions}, Algebr. Geom. Topol. 6, p.2473–2508, 2006.


\bibitem[O04]{Oancea:Survey}
A. Oancea, \textit{A survey of Floer homology for manifolds with contact type boundary or symplectic homology}, Ensaios Mat., 7, p.51–91, 2004.

\bibitem[Oh96]{Oh:LagPert}
Y.G. Oh, \textit{Fredholm theory of holomorphic discs under the perturbation of boundary conditions}, Math. Z., Vol. 222, p.505–520, 1996.

\bibitem[OO05]{OO:Filling} 
H. Ohta and K. Ono, \textit{Simple singularities and symplectic fillings}, J. Differential
Geom. 69, no. 1, p.1–42, 2005.

\bibitem[O05]{Ozbagci:Stabilization}
B. Ozbagci, \textit{A note on contact surgery diagrams}, Int. J. Math., Volume 16, Number 1, p.87-99, 2005.

\bibitem[O09]{Ozbagci:CotangentBundle}
B. Ozbagci, \textit{Stein and Weinstein structures on disk cotangent bundles of surfaces}, Archiv der Mathematik, Volume 113, Issue 6, p.661–670, 2019.

\bibitem[OS04]{OS:SurgeryBook}
B. Ozbagci and A. I. Stipsicz, \textit{Surgery on contact 3-manifolds and Stein surfaces}, Bolyai Society Mathematical Studies,Springer-Verlag, Volume 13, 2004.

\bibitem[OzvSz04]{OS:HF}
P. Ozsv{\'a}th and Z. Szab{\'o}, \textit{Holomorphic disks and topological invariants for closed three-manifolds}, Ann. of Math. (2) 159, p.1027–1158, 2004.

\bibitem[OzvSz05]{OS:ContactClass}
P. Ozsv{\'a}th and Z. Szab{\'o}, \textit{Heegaard Floer homology and contact structures}, Duke Math. J. 129, p.39–61, 2005.

\bibitem[P12]{Pardon:HFLecture}
J. Pardon, \textit{Obstruction bundles and counting holomorphic disks in Heegaard Floer homology}, lecture at the Symplectic and Low Dimensional Topologies in Interaction workshop at the Simons Center for Geometry and Physics, \url{http://scgp.stonybrook.edu/video_portal/video.php?id=490}, 2012.

\bibitem[Pard19]{Pardon:Contact}
J. Pardon, \textit{Contact homology and virtual fundamental cycles}, J. Amer. Math. Soc. 32, no. 3, p.825-919, 2019.

\bibitem[Park05]{Parker:Thesis}
B. Parker, \textit{Holomorphic curves in Lagrangian torus fibrations}, Ph.D thesis, Stanford University, 2005.

\bibitem[Pla07]{Olga:CombinatorialCHF}
O. Plamenevskaya, \textit{A combinatorial description of the Heegaard Floer contact invariant},
Algebr. Geom. Topol. 7, p.1201–1209, 2007.

\bibitem[Ra10]{Ras:MilnorConj}
J. Rasmussen, \textit{Khovanov homology and the slice genus}, Invent. math., volume 182, p.419–447, 2010.

\bibitem[Ro90]{Rolfsen}
D. Rolfsen, \textit{Knots and links} (Corrected reprint of the 1976 original), Mathematics Lecture Series, Vol. 7, Publish or Perish Inc., Houston, TX, 1990.


\bibitem[RS93]{RS:Index}
J. Robbin and D. Salamon, \textit{The Maslov index for paths}, Topology 32, Number 4, p.827–844, 1993.


\bibitem[RS01]{RS:Strips}
J. Robbin and D. Salamon, \textit{Asymptotic behavior of holomorphic strips}, Ann. Inst. H. Poincar\'{e} Anal. Non Lin\'{e}aire, p.573–612, 2001.


\bibitem[Ro19]{Rooney:ECH}
J. Rooney, \textit{Cobordism maps in embedded contact homology}, arXiv:1912.01048, 2019.


\bibitem[Ru97]{Rudolph}
L. Rudolph, \textit{The slice genus and the Thurston–Bennequin invariant of a knot}, Proc. Amer. Math. Soc., Volume 125, p.3049–3050, 1997.

\bibitem[Sa99]{Salamon:HamtonianLectures}
D. Salamon, \textit{Lectures on Floer homology}. Symplectic geometry and topology (Park City, UT, 1997), 143–229, IAS/Park City Math. Ser., 7, Amer. Math. Soc., Providence, RI, 1999.


\bibitem[SW10]{SarkarWang}
S. Sarkar and J. Wang \textit{An algorithm for computing some Heegaard Floer homologies}, Ann Math 171, p.1213–1236, 2010.


\bibitem[Sc93]{Schwarz:Morse}
M. Schwarz, \textit{Morse homology}, Progress in Mathematics, vol. 111, Birkh{\"a}user, Basel, 1993

\bibitem[Sc95]{Schwarz:Thesis}
M. Schwarz, \textit{Cohomology operations from $\Circle$ cobordisms in Floer homology}, PhD thesis, ETH Zurich, 1995.


\bibitem[Se07]{BiasedSH}
P. Seidel, \textit{A biased view of symplectic cohomology}, arXiv:math/0704.2055, 2007.

\bibitem[Si19]{Siegel:RSFT}
K. Siegel, \textit{Higher symplectic capacities}, arXiv:1902.01490, 2019

\bibitem[S08]{Siefring:Asymptotics}
R. Siefring, \textit{Relative asymptotic behavior of pseudoholomorphic half-cylinders}, Comm. Pure
Appl. Math. 61, p.1631–1684, 2008.

\bibitem[S13]{Sivek:NoAugs}
S. Sivek, \textit{The contact homology of Legendrian knots with maximal
Thurston-Bennequin invariant}, J. Symp. Geom., Vol. 11, p.167–178, 2013.

\bibitem[S]{Sivek:Code}
S. Sivek, \textit{lch.sage}, software available at \url{https://www.ma.imperial.ac.uk/~ssivek/code/lch.sage}.

\bibitem[Sm62]{Smale:HCobordism}
S. Smale, \textit{On the structure of manifolds}, Amer. Journ. Math., Number 3, p.387-399, 1962.

\bibitem[Su05]{Sullivan:Coproduct}
D. Sullivan, \textit{Sigma models and string topology in Graphs And Patterns}, in Mathematics And Theoretical
Physics: Proceedings Of The Stony Brook Conference On Graphs And Patterns In Mathematics And Theoretical Physics, Dedicated to Dennis Sullivan’s 60th Birthday Proceedings of Symposia in Pure Mathematics,
American Mathematical Society, 2005.

\bibitem[T97]{Traynor:Helix}
L. Traynor, \emph{Legendrian circular helix links}, Mathematical Proceedings of the Cambridge Philosophical Society 122, p.301-314, 1997.


\bibitem[V15]{Vaugon:Bypass}
A. Vaugon, \textit{Reeb periodic orbits after a bypass attachment}, Ergod. Th. Dynam. Sys. 35, p. 615-672, 2015.

\bibitem[V99]{Viterbo:SH}
C. Viterbo, \textit{Functors and computations in Floer homology with applications, Part I}, Geom.
Funct. Anal. 9, p.985–1033, 1999.


\bibitem[W15]{Wand:LegendrianSurgery}
A. Wand, \textit{Tightness is preserved by Legendrian surgery}, Ann. of Math., Volume 128, Issue 2, p.723-738, 2015.


\bibitem[Wa83]{Warner}
F. W. Warner, \textit{Foundations of differentiable manifolds and Lie groups}, Graduate Texts in Mathematics 94, Springer-Verlag, 1983.

\bibitem[Wei91]{Weinstein:Handles}
A. Weinstein, \textit{Contact surgery and symplectic handlebodies}, Hokkaido Math. J., Vol. 20, p.241-251, 1991.

\bibitem[Wen10a]{Wendl:Automatic}
C. Wendl, \textit{Automatic transversality and orbifolds of punctured holomorphic curves in dimension four}, Comment. Math. Helv. 85, no. 2, p.347-407, 2010.

\bibitem[Wen10b]{Wendl:OB}
C. Wendl, \textit{Open book decompositions and stable Hamiltonian structures}, Expo. Math., Vol. 28, p.187-199, 2010.

\bibitem[Wen10c]{Wendl:Foliations}
C. Wendl, \textit{Strongly fillable contact manifolds and J-holomorphic foliations}, Duke Math. J., Volume 151, Number 3, p.337-384, 2010.

\bibitem[Wen10]{Wendl:SHSurvey}
C. Wendl, \textit{A beginners overview of symplectic homology}, Lecture notes available at \url{https://www.mathematik.hu-berlin.de/~wendl/pub/SH.pdf}

\bibitem[Wen13]{Wendl:Torsion}
C. Wendl, \textit{A hierarchy of local symplectic filling obstructions for contact 3-manifolds}, Duke Math. J., Vol. 162, p.2197–2283, 2013.

\bibitem[Wen13]{Wendl:NonExact}
C. Wendl, \textit{Non-exact symplectic cobordisms between contact 3-manifolds}. Journal of Differential Geometry, Volume 95, p.121–182, 2013.

\bibitem[Wen15]{Wendl:Signs}
C. Wendl, \textit{Signs (or how to annoy a symplectic topologist}, blog post available at \url{https://symplecticfieldtheorist.wordpress.com/2015/08/23/signs-or-how-to-annoy-a-symplectic-topologist/}, 2015.


\bibitem[Wen16]{Wendl:SFTNotes}
C. Wendl, \textit{Lectures on Symplectic Field Theory}, arXiv:1612.01009, 2016.

\bibitem[Wi82]{Witten:Morse}
E. Witten, \textit{Supersymmetry and Morse theory}, J. Differential Geom. 17, p.661-692, 1982.

\bibitem[Y06]{Yau:VanishingCH}
M. L. Yau, \emph{Vanishing of the contact homology of overtwisted contact 3-
manifolds (with an appendix by Y. Eliashberg)}, Bull. Inst. Math. Acad. Sin. 1, p.211–229, 2006.
\end{comment}

\end{thebibliography}


\end{document}
